

```{r eval=FALSE}

# conda activate r-env

library(Seurat)
library(tidyverse)
library(cowplot)
library(viridis)
library(ggpubr)
library(RColorBrewer)
library(ggrepel)
library(patchwork)
library(ggrastr)

theme_set(theme_cowplot())
prediction.colfunc <- colorRampPalette(rev(brewer.pal(9, 'Purples' )[2:9]))
colfunc <- colorRampPalette(rev(brewer.pal(9, 'Greens' )[2:9]))


setwd("/Volumes/GoogleDrive/Shared drives/Bioinfo_SwarupLab/Sam_Dropbox/pipelines/FIRE-mouse-2021/analysis")
data_dir <- "data/"
fig_dir <- 'figures/'

umap_theme <- theme(
  axis.line=element_blank(),
  axis.text.x=element_blank(),
  axis.text.y=element_blank(),
  axis.ticks=element_blank(),
  axis.title.x=element_blank(),
  axis.title.y=element_blank(),
  panel.background=element_blank(),
  panel.border=element_blank(),
  panel.grid.major=element_blank(),
  panel.grid.minor=element_blank(),
  plot.background=element_blank()
)


```

barplot showing the number of cells in each cluster:


```{r eval=FALSE}

df <- as.data.frame(table((seurat_obj$clusternum_anno)))
df$Var1 <- fct_rev(df$Var1)

p1 <- ggplot(df, aes(x=Var1, y=Freq, fill=Var1)) +
  geom_bar(stat='identity') + NoLegend() + RotatedAxis() + ylab(expression(italic(N)[cells])) + xlab('') +
  geom_text(aes(label=scales::comma(Freq, accuracy=1)),  color="black", size=3.5, hjust='inward') +
  scale_y_continuous(labels=scales::comma) +
  coord_flip() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.minor=element_blank(),
    panel.grid.major.x=element_line(colour="lightgray", size=0.5),
    axis.ticks.x=element_blank(),
  )

pdf('barplot_nCells.pdf', width=4, height=8)
p1
dev.off()


df <- as.data.frame(table((seurat_obj$clusternum_anno)))
df$Var1 <- fct_rev(df$Var1)

p1 <- ggplot(df, aes(x=Var1, y=Freq, fill=Var1)) +
  geom_bar(stat='identity') + NoLegend() + RotatedAxis() + ylab(expression(italic(N)[cells])) + xlab('') +
  geom_text(aes(label=scales::comma(Freq, accuracy=1)),  color="black", size=3.5, hjust='inward') +
  scale_y_continuous(labels=scales::comma) +
  scale_fill_manual(values=cluster_colors_all) +
  coord_flip() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.minor=element_blank(),
    panel.grid.major.x=element_line(colour="lightgray", size=0.5),
    axis.ticks.x=element_blank(),
  )


pdf(paste0(fig_dir, 'barplot_nCells_clusters.pdf'), width=4, height=8)
p1
dev.off()

```

Dotplot of cluster DEGs:

```{r eval=FALSE}

markers <- c(
  'Rarb',
  'Trpc6',
  'Shisa6',
  'Igfn1',
  'Ndst4',
  'Cux2',
  'Hs3st2',
  'Rorb',
  'Tshz2',
  'Tmem200a',
  'Grik3',
  'Kcnip1',
  'Kcnmb2',
  'Synpo2',
  'Tmem163',
  'Cpa6',
  'Pcbp3',
  'Gpc5',
  'Slc6a11',
  'Plpp3',
  'Gm29521',
  'Vcan',
  'Ddn',
  'Inpp5d',
  'Spag16',
  'Plp1',
  'Enpp6',
  'Flt1',
  'Notch3',
  'Ptgds'
)


# dot plot color scheme:
dotplot_colors <- c(rep('#FFFFFF', 50), rev(prediction.colfunc(150)))

p <- DotPlot(seurat_obj, features = rev(markers), group.by='clusternum_anno', dot.min=0.15) +
  coord_flip() + RotatedAxis() +
  scale_color_gradientn(colors=dotplot_colors) +
  ylab('') + xlab('') + ggtitle('Cluster marker DEGs') + theme(plot.title = element_text(hjust = 0.5))

pdf(paste0(fig_dir, 'dotplot_cluster_markers.pdf'), width=12, height=8, useDingbats=FALSE)
p
dev.off()


```

Plot rosenberg label transfer ordered

```{r eval=FALSE}

DefaultAssay(seurat_obj) <- 'predictions'

prediction.features <- c(

  '4 Medium Spiny Neurons',
  '40 HIPP Granule/PyrCA3',
  '35 HIPP Pyr Crym',
  '38 HIPP Pyr Grik4',
  '41 HIPP Pyr Npy2r',
  '11 CTX PyrL4/L5',
  '5 CTX PyrL2/L3 Pappa2',
  '7 CTX PyrL2/L3 Met',
  '14 CTX PyrL6a',
  '18 CLAU Pyr',
  '10 CTX PyrL4 Rorb',
  '12 CTX PyrL5 Itgb3',
  '6 CTX PyrL2/L3/L4 Ntf3',
  '15 CTX PyrL5/L6 Sulf1',
  '16 CTX PyrL5/L6 Npr3',
  '17 CTX PyrL6',
  '34 SUB Pyr',
  '13 CTX PyrL5 Fezf2',
  '19 MTt Glut',
  '32 Nigral Dopaminergic',
  '44 Migrating Int Lhx6',
  '50 Migrating Int Adarb2',
  '20 THAL Glut',
  '2 OB Mitral/Tufted Ms4a15',
  '28 CB Granule',
  '46 Migrating Int Cpa6',
  '49 Migrating Int Lgr6',
  '69 Astro Prdm16',
  '71 Bergmann Glia',
  '68 Astro Slc7a10',
  '73 OEC',
  '61 OPC',
  '59 Oligo COP1',
  '60 Oligo COP2',
  '51 SVZ Stem',
  '52 Cajal-Retzius',
  '63 Microglia',
  '62 Macrophage',
  '72 Ependyma',
  '57 Oligo MOL',
  '56 Oligo MFOL1',
  '55 Oligo MFOL2',
  '64 Endothelia',
  '65 SMC',
  '66 VLMC Slc6a13'
)


p <- DotPlot(
  seurat_obj, group.by='clusternum_anno', dot.min=0.25,
  features=rev(prediction.features)
) + coord_flip() + RotatedAxis() + scale_color_gradientn(colors=rev(colfunc(256))) + ylab('') + xlab('') + ggtitle('Seurat Label Transfer with Rosenberg et al. 2018 SPLiT-seq data') + theme(plot.title = element_text(hjust = 0.5))
pdf(paste0(fig_dir, 'dotplot_LT_predictions.pdf'), width=12, height=10, useDingbats=FALSE)
p
dev.off()


```

Csf1r depletion in FIRE conditions:

```{r eval=FALSE}

# color scheme from Sep:
sample_color.scheme <- c(
  rgb(139,171,211, maxColorValue=255),
  rgb(9,153,99, maxColorValue=255),
  rgb(176,127,192, maxColorValue=255),
  rgb(7,126,151, maxColorValue=255),
  rgb(87,87,249, maxColorValue=255),
  rgb(184,86,215, maxColorValue=255)
)
names(sample_color.scheme) <- levels(seurat_obj$DX)


comparisons <- list(c(1,2),  c(1,3), c(2,4))

# csf1r
genes <- c('Csf1r', 'Cx3cr1', 'P2ry12', 'Trem2', 'Tmem119',  'Cd9')

for(gene in genes){
  print(gene)
  p1 <- VlnPlot(subset(seurat_obj, class=='IMM'), features=gene, group.by='DX', pt.size=0) + scale_fill_manual(values=sample_color.scheme) +
  stat_compare_means(method='wilcox', comparisons=comparisons, label='p.signif') +
  xlab('') + NoLegend() + ylim(c(-0.1,4.75))
  pdf(paste0(fig_dir, 'vlnplot_', gene, '_DX.pdf'), width=4, height=4)
  print(p1)
  dev.off()

}

```


DAM scores

```{r eval=FALSE}

homeostatic <- str_to_title(c('HEXB', 'CST3', 'CX3CR1', 'CTSD', 'CSF1R', 'CTSS', 'SPARC', 'TMSB4X', 'P2RY12', 'C1QA', 'C1QB'))
stage1_DAM <- str_to_title(c('TYROBP', 'CTSB', 'APOE', 'B2M', 'FTH1'))
stage2_DAM <- str_to_title(c('TREM2', 'AXL', 'CST7', 'CTSL', 'LPL', 'CD9', 'CSF1', 'ITGAX', 'CLEC7A', 'LILRB4', 'TIMP2'))

seurat_imm <- subset(seurat_obj, class == 'IMM')

seurat_imm <- AddModuleScore(
  seurat_imm,
  features=list('stage1_DAM'=stage1_DAM, 'stage2_DAM'=stage2_DAM, 'homeostatic'=homeostatic),
  name=c('stage1_DAM', 'stage2_DAM', 'homeostatic')
)


comparisons <- list(c(5,6), c(2,4), c(1,3), c(1,2), c(1,6))

p1 <- VlnPlot(seurat_imm, features='homeostatic3', group.by='DX', pt.size=0) + scale_fill_manual(values=sample_color.scheme) +
geom_hline(yintercept = 0, linetype='dashed') +
stat_summary(fun.data='mean_cl_boot', color='black') +
stat_compare_means(method='wilcox', comparisons=comparisons, label='p.signif') +
xlab('') + NoLegend() +
ylim(c(-0.5,2.5))+ ggtitle('Homeostatic')

p2 <- VlnPlot(seurat_imm, features='stage1_DAM1', group.by='DX', pt.size=0) + scale_fill_manual(values=sample_color.scheme) +
geom_hline(yintercept = 0, linetype='dashed') +
stat_summary(fun.data='mean_cl_boot', color='black') +
stat_compare_means(method='wilcox', comparisons=comparisons, label='p.signif') +
xlab('') + NoLegend() +
ylim(c(-0.5,2.5))+ ggtitle('Stage 1 DAM')

p3 <- VlnPlot(seurat_imm, features='stage2_DAM2', group.by='DX', pt.size=0) + scale_fill_manual(values=sample_color.scheme) +
geom_hline(yintercept = 0, linetype='dashed') +
stat_summary(fun.data='mean_cl_boot', color='black') +
stat_compare_means(method='wilcox', comparisons=comparisons, label='p.signif') +
xlab('') + NoLegend() +
ylim(c(-0.5,2.5)) + ggtitle('Stage 2 DAM')

pdf(paste0(fig_dir, 'vlnplot_DAM_DX.pdf'), width=8, height=4, useDingbats=FALSE)
p1 | p2 | p3
dev.off()


```

categorical variables:

Plot barplot for each cluster showing proportion of genotype, Sex, etc:

```{r eval=FALSE}

################################################################################
# Proportion of Sample in each cluster
################################################################################

seurat_meta <- seurat_obj@meta.data
seurat_meta$SampleID <- droplevels(seurat_meta$SampleID)

samples <- seurat_obj$SampleID %>% unique %>% as.character

clusters <- seurat_obj$clusternum_anno %>% levels %>% as.character


proportion_df <- data.frame()
for(i in 1:length(clusters)){
  cluster_meta <- subset(seurat_meta, clusternum_anno == clusters[i])
  cur_df <- as.data.frame(table(cluster_meta$SampleID)/dim(cluster_meta)[1])
  print(sum(cur_df$Freq))
  cur_df$cluster <- clusters[i]
  proportion_df <- rbind(proportion_df, cur_df)
}

proportion_df <- dplyr::rename(proportion_df, SampleID = Var1)
proportion_df <- dplyr::rename(proportion_df, fraction = Freq)
proportion_df$cluster <- factor(proportion_df$cluster, levels=levels(seurat_obj$clusternum_anno))

pdf("figures/sample_clusters_barplot.pdf", height=4, width=10)
p <- ggplot(proportion_df, aes(y=fraction, x=cluster, fill=SampleID)) +
  geom_bar(stat='identity') +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_manual(values=color.scheme) +
  #theme_minimal() +
  theme(
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    axis.text.x = element_text(angle=45, hjust=1),
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_blank()
  ) + NoLegend()
print(p)
dev.off()

################################################################################
# Proportion of Sex in each cluster
################################################################################
seurat_meta <- seurat_obj@meta.data
seurat_meta$SampleID <- droplevels(seurat_meta$SampleID)

clusters <- seurat_obj$clusternum_anno %>% unique %>% as.character

proportion_df <- data.frame()
for(i in 1:length(clusters)){
  cluster_meta <- subset(seurat_meta, clusternum_anno == clusters[i])
  cur_df <- as.data.frame(table(cluster_meta$Sex)/dim(cluster_meta)[1])
  print(sum(cur_df$Freq))
  cur_df$cluster <- clusters[i]
  proportion_df <- rbind(proportion_df, cur_df)
}

proportion_df <- dplyr::rename(proportion_df, Sex = Var1)
proportion_df <- dplyr::rename(proportion_df, fraction = Freq)
proportion_df$cluster <- factor(proportion_df$cluster, levels=levels(seurat_obj$clusternum_anno))


pdf("figures/sex_clusters_barplot.pdf", height=4, width=10)
p <- ggplot(proportion_df, aes(y=fraction, x=cluster, fill=Sex)) +
  geom_bar(stat='identity') +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_manual(values=c("goldenrod1", "dodgerblue")) +
  #theme_minimal() +
  theme(
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    axis.text.x = element_text(angle=45, hjust=1),
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_blank()
  )
print(p)
dev.off()


```


```{r eval=FALSE}

################################################################################
# number of cells in each sample
#################################################################################

seurat_obj$SampleID <- droplevels(seurat_obj$SampleID)


df <- as.data.frame(table(seurat_obj$SampleID))
df$group <- factor(
  as.character(seurat_obj@meta.data$DX)[match(as.character(df$Var1), seurat_obj@meta.data$SampleID)],
  levels = levels(seurat_obj$DX)
)

p <- ggplot(df, aes(x=reorder(Var1, Freq), y=Freq, fill=Var1, )) +
  geom_bar(stat='identity') +
  geom_text(aes(label=scales::comma(Freq, accuracy=1)),  color="black", size=3.5, hjust='inward') +
  scale_y_continuous(labels=scales::comma) +
  scale_fill_manual(values=color.scheme) +
  coord_flip() + NoLegend() + RotatedAxis() + xlab('') +  ylab(expression(italic(N)[cells])) +
  ggtitle('Number of cells per sample in each condition') + theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.minor=element_blank(),
    panel.grid.major.x=element_line(colour="lightgray", size=0.5),
    axis.ticks.y=element_blank(),
  )

pdf(paste0(fig_dir, 'barplot_nCells_samples.pdf'), width=6, height=6)
p + facet_wrap(~group, scales='free_y', ncol=2)
dev.off()


```

UMAP colored by sample and sex:

```{r eval=FALSE}


################################################################################
# UMAP colored by sample:
#################################################################################

p1 <- seurat_obj@meta.data %>% ggplot(aes(x=UMAP_1, y=UMAP_2, color=SampleID)) +
  rasterise(geom_point(size=0.5), dpi=800) +
  scale_color_manual(values=color.scheme) +  umap_theme + guides(color = guide_legend(override.aes = list(size=3)))


pdf(paste0(fig_dir, 'umap_samples.pdf'), width=7, height=6, useDingbats=FALSE)
p1 + facet_wrap('DX', ncol=2) + theme(strip.background=element_blank())
dev.off()

################################################################################
# UMAP colored by Sex
#################################################################################

p1 <- seurat_obj@meta.data %>% ggplot(aes(x=UMAP_1, y=UMAP_2, color=Sex)) +
  rasterise(geom_point(size=0.5), dpi=800) +
  scale_color_manual(values=c('goldenrod1', 'dodgerblue')) +  umap_theme + guides(color = guide_legend(override.aes = list(size=3)))


pdf(paste0(fig_dir, 'umap_sex.pdf'), width=7, height=6, useDingbats=FALSE)
p1
dev.off()

```

Violin plot of UMI for each sample and each cluster:

```{r eval=FALSE}

p1 <- VlnPlot(seurat_obj, features='nCount_RNA', group.by='SampleID', pt.size=0) + scale_fill_manual(values=color.scheme) +
geom_boxplot(outlier.shape=NA, width=.25, fill='white') +
scale_y_continuous(labels=scales::comma) +
ylab(expression(italic(N)[UMI])) +
xlab('') + NoLegend() + ggtitle('')

pdf('figures/vlnplot_nUMI_samples.pdf', width=8, height=3)
p1
dev.off()



p1 <- VlnPlot(seurat_obj, features='nCount_RNA', group.by='clusternum_anno', pt.size=0) + scale_fill_manual(values=cluster_colors_all) +
geom_boxplot(outlier.shape=NA, width=.25, fill='white') +
scale_y_continuous(labels=scales::comma) +
ylab(expression(italic(N)[UMI])) +
xlab('') + NoLegend() + ggtitle('')

pdf('figures/vlnplot_nUMI_clusters.pdf', width=9, height=4)
p1
dev.off()


```

boxplot showing proportions

```{r eval=FALSE}


#################################################################################
# Proportion of clusters
#################################################################################

seurat_obj$class <- droplevels(seurat_obj$class)

seurat_meta <- seurat_obj@meta.data %>% subset(class %in% c('INH', 'EX', 'OB')); name='neuronal'; w=6;h=10; group='clusternum_anno';
seurat_meta <- seurat_obj@meta.data %>% subset(!class %in% c('INH', 'EX', 'OB'));  name='non-neuronal'; w=6;h=10; group='clusternum_anno';


seurat_meta <- seurat_obj@meta.data %>% subset(!class %in% c('INH', 'EX', 'OB')); name='celltypes_non-neuronal'; w=6;h=10; group='class'
seurat_meta <- seurat_obj@meta.data %>% subset(class %in% c('INH', 'EX', 'OB')); name='celltypes_neuronal'; w=6;h=10; group='cluster_name'



seurat_meta$class <- seurat_meta$class %>% droplevels
seurat_meta$DX <- droplevels(seurat_meta$DX)
seurat_meta$SampleID <- droplevels(seurat_meta$SampleID)
seurat_meta$cluster_name <- seurat_meta$cluster_name %>% droplevels



meta_list <- seurat_meta%>%
  dplyr::group_split(SampleID)

temp <- lapply(meta_list, function(meta){
  df <- as.data.frame(meta[,group] %>% table / nrow(meta))
  colnames(df) <- c('cluster', 'proportion')
  df$SampleID <- unique(meta$SampleID)
  df$DX <- unique(meta$DX)
  df
})

proportion_df <- Reduce(rbind, temp)

# order clusters based on number of nucleu
proportion_df$cluster_num <- as.numeric(proportion_df$cluster)



pdf(paste0(fig_dir, name,'_composition_boxplot.pdf'), width=4, height=3)
plot_list <- list()
for(cl in unique(proportion_df$cluster)){
  cur_df <- subset(proportion_df, cluster==cl)
  #m_df <- cur_df %>% group_by(DX) %>% summarize(median = mean(proportion))


  p <- ggplot(cur_df, aes(y=proportion, x=reorder(DX, DX), fill=DX)) +
    scale_x_discrete(limits=rev(levels(cur_df$DX))) +
    geom_boxplot(outlier.shape=NA, color='black', alpha=0.7) +
    geom_jitter(aes(color=SampleID), size=1.5, width=0.25) +
    scale_fill_manual(values=sample_color.scheme) +
    scale_color_manual(values=color.scheme) +
    ggtitle(cl) +
    coord_flip() +
    labs(fill='') + NoLegend() +
    theme(
      plot.title = element_text(hjust = 0.5),
      panel.grid.major.x=element_line(colour="lightgray", size=0.5),
      axis.line.y = element_blank(),
      axis.ticks.y = element_blank()
    ) + xlab('') + ylab(paste('proportion', name))

  print(p)
  plot_list[[cl]] <- p
}
dev.off()



p <- ggplot(proportion_df, aes(y=proportion, x=reorder(cluster,-cluster_num), fill=DX)) +
  # scale_x_discrete(limits=rev(levels(cur_df$DX))) +
  geom_boxplot(outlier.shape=NA, color='black', alpha=0.7) +
  #geom_jitter(aes(color=SampleID), size=1.5, width=0.25) +
  scale_fill_manual(values=sample_color.scheme) +
  scale_color_manual(values=color.scheme) +
  coord_flip() +
  labs(fill='') + NoLegend() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.major.x=element_line(colour="lightgray", size=0.5),
    axis.line.y = element_blank(),
    axis.ticks.y = element_blank()
  ) + xlab('') + ylab(paste('proportion', name))



pdf(paste0(fig_dir, name,'_composition_boxplot_combined.pdf'), width=3, height=8)
p
dev.off()

#################################################################################
# bootstrapped cluster proportion analysis
#################################################################################


meta_list <- seurat_obj@meta.data %>%
  dplyr::group_split(SampleID)




sample_percent=0.30
n_iterations = 20

proportion_df <- data.frame()
for(i in 1:n_iterations){
  cur_sample <- seurat_meta[sample(rownames(seurat_meta), round(sample_percent*nrow(seurat_meta))),]

  meta_list <- cur_sample %>%
    dplyr::group_split(SampleID)

  temp <- lapply(meta_list, function(meta){
    #print(table(meta$Diagnosis))
    df <- as.data.frame(meta[,group] %>% table / nrow(meta))
    colnames(df) <- c('cluster', 'proportion')
    df$SampleID <- unique(meta$SampleID)
    df$DX <- unique(meta$DX)
    df
  })

  cur_df <- Reduce(rbind, temp)
  cur_df$iteration <- i
  proportion_df <- rbind(proportion_df, cur_df)
}

clusters <- unique(seurat_meta[,group])
clusters <- clusters[order(clusters)] %>% as.character()


# iteratively make comparisons:
comparisons <- list(
  '5xFIRE vs 5xFAD' = c('5xFIRE', '5xFAD'),
  'WT vs FIRE' = c('WT', 'FIRE'),
  'FIRE vs 5xFIRE' = c('FIRE', '5xFIRE')
)

result_table <- data.frame()
for(i in 1:length(comparisons)){

  cur_comparison <- comparisons[[i]]
  pvals <- sapply(clusters, function(cur_cluster){
    result <- wilcox.test(
      proportion_df %>% subset(DX==cur_comparison[1] & cluster==cur_cluster) %>% .$proportion,
      proportion_df %>% subset(DX==cur_comparison[2] & cluster==cur_cluster) %>% .$proportion
    )
    result$p.value
  })
  cur_result_table <- data.frame(
    pval = as.numeric(pvals),
    cluster = names(pvals),
    comparison = names(comparisons)[i]
  )
  result_table <- rbind(result_table, cur_result_table)
}

# compute fdr:
result_table$FDR <- p.adjust(result_table$pval, method='fdr')
result_table$signif <- as.character(gtools::stars.pval(result_table$FDR))
write.csv(result_table, file=paste0('data/', name, '_comparison_results.csv'), quote=FALSE)

result_table


```
