

## Load data from all 6 samples into here:

```{r eval=FALSE}

# in bash terminal:
# conda activate spatial
library(Seurat)
library(tidyverse)
library(cowplot)
library(Matrix)
library(viridis)
library(harmony)
library(ggpubr)
library(DoubletFinder)
library(RColorBrewer)
library(ggrepel)
library(patchwork)
colfunc <- colorRampPalette(rev(brewer.pal(11, 'Spectral' )))
prediction.colfunc <- colorRampPalette(rev(brewer.pal(9, 'Purples' )[2:9]))

theme_set(theme_cowplot())

setwd("/dfs3b/swaruplab/smorabit/analysis/FIRE_mouse_2021/4-conditions/")

# directories
data_dir <- "data/"
fig_dir <- 'figures/'

umap_theme <- theme(
  axis.line=element_blank(),
  axis.text.x=element_blank(),
  axis.text.y=element_blank(),
  axis.ticks=element_blank(),
  axis.title.x=element_blank(),
  axis.title.y=element_blank(),
  panel.background=element_blank(),
  panel.border=element_blank(),
  panel.grid.major=element_blank(),
  panel.grid.minor=element_blank(),
  plot.background=element_blank()
)

# re-load 4 condition data
seurat_obj <- readRDS('data/FIRE_mouse_seurat_4_conditions.rds')
DefaultAssay(seurat_obj) <- 'RNA'



# re-load 6 condition data:
seurat_obj <- readRDS('/dfs3b/swaruplab/smorabit/analysis/FIRE_mouse_2021/data/FIRE_mouse_seurat.rds')

# remove unwanted clusters (unknown & odc/vlmc)
seurat_obj <- seurat_obj[,!(seurat_obj$clusternum_anno %in% c('42-UNK', '44-VLMC / ODC'))]

# subset to remove the transplant conditions:
seurat_obj <- subset(seurat_obj, DX %in% c('WT', 'FIRE', '5xFAD', '5xFIRE'))

# color scheme for samples:
color.scheme <- c(
  brewer.pal(9, 'Reds')[2:9],
  brewer.pal(9, 'Purples')[2:9],
  brewer.pal(9, 'Oranges')[2:9],
  brewer.pal(9, 'Greys')[2:9],
  brewer.pal(9, 'Blues')[2:9],
  brewer.pal(9, 'Greens')[2:9]
)
names(color.scheme) <- as.character(levels(seurat_obj$SampleID))

sample_color.scheme <- c(
  brewer.pal(9, 'Greys')[5],
  brewer.pal(9, 'Purples')[7],
  brewer.pal(9, 'Oranges')[6],
  brewer.pal(9, 'Reds')[6],
  brewer.pal(9, 'Blues')[5],
  brewer.pal(9, 'Greens')[5]
)
names(sample_color.scheme) <- levels(seurat_obj$DX)

```

Re-process data with only 4 conditions:

```{r eval=FALSE}


seurat_obj <- FindVariableFeatures(seurat_obj, nfeatures=3500)
VariableFeatures(seurat_obj) <- VariableFeatures(seurat_obj)[!grepl("^mt-", VariableFeatures(seurat_obj))]

# dim reduction
seurat_obj <- RunPCA(seurat_obj, features=VariableFeatures(seurat_obj))
seurat_obj <- RunHarmony(seurat_obj, dims=1:30, group.by='SampleID')
seurat_obj <- RunUMAP(seurat_obj, reduction='harmony', dims = 1:30, n.neighbors=15L, min.dist=0.10)

# clustering
seurat_obj <- FindNeighbors(seurat_obj, dims=1:30, reduction='harmony', annoy.metric='cosine')
seurat_obj <- FindClusters(seurat_obj, resolution = 0.25)

#################################################################################
# plot UMAP
#################################################################################

# plotting initial clusters from Seurat:
p1 <- DimPlot(seurat_obj, group.by='seurat_clusters', label=TRUE) + umap_theme + NoLegend() + ggtitle('seurat clusters') + theme(plot.title = element_text(hjust = 0.5))

p2 <- DimPlot(seurat_obj, group.by='class', label=TRUE) + umap_theme + NoLegend() + ggtitle('annotations from full data') + theme(plot.title = element_text(hjust = 0.5))


pdf(paste0(fig_dir, 'umap_seurat_initial_clusters.pdf'), width=10, height=5)
p1 + p2
dev.off()

#################################################################################
# save data for scanpy:
#################################################################################


# save data matrix:
X <- GetAssayData(seurat_obj, assay='RNA', slot='data')
Matrix::writeMM(X, file=paste0(data_dir, 'FIRE_mouse_normCounts.mtx'))



# save gene names:
write.table(
  data.frame('gene'=rownames(X)),
  file=paste0(data_dir, 'gene_names.csv'),
  quote=F,
  row.names=F,
  col.names=F
)

# save harmony matrix as csv
write.csv(seurat_obj@reductions$harmony@cell.embeddings, file=, paste0(data_dir, 'FIRE_mouse_harmony.csv'), quote=F, row.names=F)

# save metadata:
meta <- seurat_obj@meta.data
meta$barcode <- colnames(seurat_obj)
meta$UMAP1 <- seurat_obj@reductions$umap@cell.embeddings[,1]
meta$UMAP2 <- seurat_obj@reductions$umap@cell.embeddings[,2]

write.csv(meta, file=paste0(data_dir, 'FIRE_mouse_meta.csv'), quote=F, row.names=F)




```

Compute UMAP & clusters with scanpy:

```{python eval=FALSE}


import scanpy as sc
import anndata
from scipy import io
from scipy.sparse import coo_matrix, csr_matrix
import numpy as np
import seaborn as sns
from matplotlib import pyplot as plt
import os
import pandas as pd

data_dir = "data/"
fig_dir = "figures/"

# load sparse matrix:
X = io.mmread("{}FIRE_mouse_normCounts.mtx".format(data_dir))

# create anndata object
adata = anndata.AnnData(
    X=X.transpose().tocsr()
)

# load sample metadata:
sample_meta = pd.read_csv("{}FIRE_mouse_meta.csv".format(data_dir))

# load gene names:
with open("{}gene_names.csv".format(data_dir), 'r') as f:
    gene_names = f.read().splitlines()

adata.obs = sample_meta
adata.obs.index = adata.obs['barcode']
adata.obs = adata.obs.drop(labels='barcode', axis=1)
adata.var.index = gene_names

# load pca:
pca = pd.read_csv("{}FIRE_mouse_harmony.csv".format(data_dir))
pca.index = adata.obs.index

# set pca and umap
adata.obsm['X_pca'] = pca.to_numpy()
adata.obsm['X_umap'] = np.vstack((adata.obs['UMAP1'].to_numpy(), adata.obs['UMAP2'].to_numpy())).T

# compute umap with scanpy:
sc.pp.neighbors(adata, n_neighbors=15, n_pcs=30, metric='cosine')
sc.tl.umap(adata, min_dist=0.1)
sc.pl.umap(adata, color='DX', save='_scanpy.pdf', frameon=False)

# correct with PAGA:
sc.pp.neighbors(adata, n_neighbors=15, n_pcs=30, metric='cosine')
sc.tl.leiden(adata, resolution=1.5)
adata.obs['leiden_res1.5'] = adata.obs['leiden']
sc.tl.paga(adata)
sc.pl.paga(
    adata, threshold=0.3, title='', edge_width_scale=0.5,
    frameon=False, save=True
)

# re-compute UMAP
sc.tl.umap(adata, min_dist=0.15, init_pos='paga')
sc.pl.umap(adata, color=['leiden'], save='_paga_leiden.pdf', frameon=False, legend_loc='on data')
sc.pl.umap(adata, color=['clusternum_anno'], save='_paga_old_clusters.pdf', frameon=False)

# compute low-res leiden clusters
sc.tl.leiden(adata, resolution=0.7)
adata.obs['leiden_res0.7'] = adata.obs['leiden']

# compare scanpy clusters with seurat clusters:
sc.pl.umap(adata, color=['clusternum_anno', 'leiden_res0.7', 'leiden_res1.5'], save='_paga_compare_clusters.pdf', frameon=False, legend_loc='on data')

# save anndata object
adata.write('{}FIRE_mouse_scanpy.h5ad'.format(data_dir))

# save cluster assignments and UMAP coordinates for Seurat
adata.obs['paga_UMAP1'] = adata.obsm['X_umap'][:,0]
adata.obs['paga_UMAP2'] = adata.obsm['X_umap'][:,1]
adata.obs.to_csv('{}scanpy_meta.csv'.format(data_dir))


```


Transfer this scanpy data over to Seurat obj:
```{r eval=FALSE}

scanpy_meta <- read.csv(paste0(data_dir,'scanpy_meta.csv'))
seurat_obj$leiden_res0.7 <- factor(scanpy_meta$leiden_res0.7, levels=min(scanpy_meta$leiden_res0.7):max(scanpy_meta$leiden_res0.7))
seurat_obj$leiden_res1.5 <- factor(scanpy_meta$leiden_res1.5, levels=min(scanpy_meta$leiden_res1.5):max(scanpy_meta$leiden_res1.5))
# Idents(seurat_obj) <- seurat_obj$leiden_res0.7

paga_umap <- as.matrix(select(scanpy_meta, c(paga_UMAP1, paga_UMAP2)))
rownames(paga_umap) <- colnames(seurat_obj)
seurat_obj@reductions$paga_umap <-  CreateDimReducObject(
    embeddings=paga_umap,
    key="umap_",
    assay="RNA"
)

# save seurat obj:
saveRDS(seurat_obj, paste0(data_dir, 'FIRE_mouse_seurat_4_conditions.rds'))

# UMAP + Clusters
p1 <- DimPlot(seurat_obj, label=TRUE, reduction='paga_umap', group.by='leiden_res0.7') + umap_theme + NoLegend()
p2 <- DimPlot(seurat_obj, label=TRUE, reduction='paga_umap', group.by='leiden_res1.5') + umap_theme + NoLegend()
p3 <- DimPlot(seurat_obj, label=TRUE, reduction='paga_umap', group.by='clusternum_anno') + umap_theme + NoLegend()

pdf(paste0(fig_dir, 'umap_clusters_leiden.pdf'), width=7, height=7)
p1
p2
p3
dev.off()

pdf(paste0(fig_dir, 'umap_clusters_leiden_big.pdf'), width=14, height=7)
p2 +p3
dev.off()



```

Plot label transfer results:



Plot prediction scores:

```{r eval=FALSE}


dir.create(paste0(fig_dir, 'rosenberg_label_transfer'))

# Plot prediction scores for some clusters:
DefaultAssay(seurat_obj) <- "predictions"
prediction_matrix <- GetAssayData(seurat_obj, assay='predictions')

p1 <- DimPlot(seurat_obj, label=TRUE, group.by='leiden_res1.5', reduction='paga_umap') + umap_theme + NoLegend()
for(label in rownames(seurat_obj)[rowSums(prediction_matrix) > 0]){

  name <- gsub(' ', '_', label)
  name <- gsub('/', '_', label)
  print(name)

  # umap feature plot
  p2 <- FeaturePlot(seurat_obj, features=label, order=TRUE, reduction='paga_umap') +
    scale_color_gradientn(colors=colfunc(256), guide = guide_colorbar(barwidth=15, barheight=0.5, ticks=FALSE)) +
    umap_theme + theme(legend.position='bottom')


  # cluster violin plot:
  p3 <- VlnPlot(seurat_obj, features=label, pt.size=0, group.by='leiden_res1.5') +
   NoLegend() + ggtitle('') +
   ylab(paste(label, 'score')) + xlab('clusters')

  # patchwork
  patch <- (p1 + p2) / p3

  pdf(paste0(fig_dir, 'rosenberg_label_transfer/', name, '.pdf'), width=9, height=9, useDingbats=FALSE)
  print(patch + plot_layout(heights=c(2,1)))
  dev.off()
}

# DotPlot for all prediction scores:


p <- DotPlot(
  seurat_obj, group.by='leiden_res1.5',
  features=rownames(seurat_obj)[order(rownames(seurat_obj))]
) + coord_flip() + RotatedAxis() + scale_color_gradientn(colors=rev(prediction.colfunc(256))) + ylab('') + xlab('')
pdf(paste0(fig_dir, 'rosenberg_label_transfer/prediction_dotplot.pdf'), width=12, height=12, useDingbats=FALSE)
p
dev.off()


```


Cluster Annotations
```{r eval=FALSE}

annot_df <- read.csv('~/swaruplab/smorabit/analysis/FIRE_mouse_2021/4-conditions/data/FIRE_4conditions_cluster_annotation.csv',)
seurat_obj$class <- annot_df$class[match(as.numeric(as.character(seurat_obj$leiden_res1.5)), annot_df$cluster_num)]
seurat_obj$cluster_name <- annot_df$full_name[match(as.numeric(as.character(seurat_obj$leiden_res1.5)), annot_df$cluster_num)]
seurat_obj$clusternum_anno <- paste0(as.numeric(as.character(seurat_obj$leiden_res1.5)), '-', as.character(seurat_obj$cluster_name))


# remove the two unknown clusters:
seurat_obj <- seurat_obj[,seurat_obj$class != 'UNK']
seurat_obj$leiden_res1.5 <- droplevels(seurat_obj$leiden_res1.5)
seurat_obj$class <- droplevels(seurat_obj$class)
seurat_obj$cluster_name <- droplevels(seurat_obj$cluster_name)


p1 <- DimPlot(seurat_obj, group.by='clusternum_anno', label=TRUE, repel=TRUE, reduction='paga_umap') + umap_theme +
  theme(legend.position='bottom')

p2 <- DimPlot(seurat_obj, group.by='cluster_name', label=TRUE, repel=TRUE, reduction='paga_umap') + umap_theme +theme(legend.position='bottom')

pdf(paste0(fig_dir, 'umap_clusters_annotated_test.pdf'), width=9, height=9)
p1 + NoLegend()
p2 + NoLegend()
dev.off()

saveRDS(seurat_obj, paste0(data_dir, 'FIRE_mouse_seurat_4_conditions.rds'))

```

Cortical layer marker genes:

```{r eval=FALSE}

#Plot rosenberg label transfer results just for cortical layers:
DefaultAssay(seurat_obj) <- 'predictions'

prediction.features <- c(
  '5 CTX PyrL2/L3 Pappa2',
  '7 CTX PyrL2/L3 Met',
  '6 CTX PyrL2/L3/L4 Ntf3',
  '9 CTX PyrL2/L3/L4 Mef2c',
  '10 CTX PyrL4 Rorb',
  '8 CTX PyrL4 Wnt5b',
  '11 CTX PyrL4/L5',
  '12 CTX PyrL5 Itgb3',
  '13 CTX PyrL5 Fezf2',
  '15 CTX PyrL5/L6 Sulf1',
  '16 CTX PyrL5/L6 Npr3',
  '14 CTX PyrL6a',
  '17 CTX PyrL6'
)


p <- DotPlot(
  subset(seurat_obj, cluster_name=='EX cortical'), group.by='clusternum_anno',
  features=prediction.features
) + coord_flip() + RotatedAxis() + scale_color_gradientn(colors=rev(prediction.colfunc(256))) + ylab('') + xlab('')
pdf(paste0(fig_dir, 'rosenberg_label_transfer/prediction_dotplot_cortical.pdf'), width=8, height=8, useDingbats=FALSE)
p
dev.off()

# plot expression of cortical marker genes:
DefaultAssay(seurat_obj) <- 'RNA'

cortical_markers <- list(
  'L2/3' = c('Rrad', 'Adamts2', 'Agmat', 'Sla', 'Macc1', 'Lrg1', 'Cux2', 'Pvrl3', 'Rasgrf2'),
  'L4' = c('Rspo1', 'Rorb')
) %>% unlist %>% as.character

# from rosenberg only:
cortical_markers <- list(
  'L2/3' = c('Ntf3', 'Cux2', 'Pvrl3', 'Rasgrf2'),
  'L2/3/4' = c('Rasgrf2', 'Rorb', 'Cux2', 'Pvrl3', 'Thsd7a'),
  'L4' = c('Rasgrf2', 'Rorb', 'Cux2', 'Pvrl3'),
  'L4/5' = c('Thsd7a'),
  'L5' = c('Rorb', 'Thsd7a', 'Sulf2', 'Kcnk2', 'Grik3', 'Etv1', 'Foxp2', 'Tle4', 'Tmem200a', 'Glra2', 'Fezf2'),
  'L6a' = c('Grik3'),
  'L5/6' = c('Sulf2', 'Grik3', 'Tle4', 'Htr1f', 'Sulf1', 'Rxfp1', 'Npr3'),
  'L6' = c('Htr1f', 'Syt6', 'Grik3', 'Foxp2', 'Tle4')
) %>% unlist %>% as.character %>% unique

cortical_markers_good <- c(
  ''
)

#cortical_markers <- c('Pappa2', 'Met', 'Ntf3', 'Mef2c', 'Rorb', 'Wnt5b','Itgb3', 'Fezf2', 'Npr3', 'Sulf1')


p <- DotPlot(
  subset(seurat_obj, cluster_name=='EX cortical'), group.by='clusternum_anno',
  features=cortical_markers
) + coord_flip() + RotatedAxis() + scale_color_gradientn(colors=rev(viridis(256))) + ylab('') + xlab('')
pdf(paste0(fig_dir, 'dotplot_cortical_markers.pdf'), width=8, height=8, useDingbats=FALSE)
p
dev.off()

# re-name cortical EX clusters:
annot_df <- data.frame(
  cluster = c(10, 8, 1, 13, 5, 17, 23, 7, 16, 31),
  annotation = c(
    'L2/3',
    'L2/3',
    'L2/3',
    'L5/6',
    'L4',
    'L5',
    'L2/3/4',
    'L5/6',
    'L5/6',
    'L5/6'
  ),
  stringsAsFactors=FALSE
)


seurat_obj$cortical_layer <- annot_df$annotation[match(as.numeric(as.character(seurat_obj$leiden_res1.5)), annot_df$cluster)]

seurat_obj$clusternum_anno <- ifelse(
  is.na(seurat_obj$cortical_layer), as.character(seurat_obj$clusternum_anno),
  paste(as.character(seurat_obj$clusternum_anno), seurat_obj$cortical_layer)
)

load(file=paste0(data_dir, 'cluster_marker_DEGs.rda'))
clusters_layers <- annot_df$annotation[match(as.numeric(do.call(rbind, strsplit(as.character(markers$cluster), '-'))[,1]), annot_df$cluster)]

markers$cluster <- ifelse(
  is.na(clusters_layers), as.character(markers$cluster),
  paste(as.character(markers$cluster), clusters_layers)
)


p1 <- DimPlot(seurat_obj, group.by='clusternum_anno', label=TRUE, repel=TRUE, reduction='paga_umap') + umap_theme +
  theme(legend.position='bottom')

pdf(paste0(fig_dir, 'umap_clusters_annotated_layers.pdf'), width=9, height=9)
p1 + NoLegend()
dev.off()


saveRDS(seurat_obj, paste0(data_dir, 'FIRE_mouse_seurat_4_conditions.rds'))


```


Plot categorical variables:

```{r eval=FALSE}

setwd("/dfs3b/swaruplab/smorabit/analysis/FIRE_mouse_2021/4-conditions/composition")

################################################################################
# number of cells of each cluster
#################################################################################
library(ggdendro)
library(egg)

df <- as.data.frame(table((seurat_obj$clusternum_anno)))

p1 <- ggplot(df, aes(x=Var1, y=Freq, fill=Var1)) +
  geom_bar(stat='identity') + NoLegend() + RotatedAxis() + ylab(expression(italic(N)[cells])) + xlab('') +
  geom_text(aes(label=scales::comma(Freq)),  color="black", size=3.5, hjust='inward') +
  scale_y_continuous(labels=scales::comma) +
  coord_cartesian(xlim = c(-1, nrow(df) + 1), expand = F) +
  coord_flip() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.minor=element_blank(),
    panel.grid.major.x=element_line(colour="lightgray", size=0.5),
    axis.ticks.x=element_blank(),
  )


p2 <- ggdendrogram(col_dend, rotate = TRUE, labels=FALSE) +
  scale_y_reverse()  + coord_cartesian(xlim = c(-1, nrow(df) + 1), ylim = c(-1, max(dendro_data(col_dend)$segments$y)), expand = F) + coord_flip() + theme_dendro()


pdf(paste0(fig_dir, 'barplot_nCells_clusters.pdf'), width=6, height=8)
p2 + p1 + plot_layout(widths=c(1,2))
# ggarrange(p2, p1, ncol=2, widths=c(1,2))
dev.off()

```



 DotPlot of top 20 genes for each cluster:

```{r eval=FALSE}
# 28, 36, 51, 52
load(file=paste0(data_dir, 'cluster_marker_DEGs.rda')

dir.create(paste0(fig_dir, 'marker_DEGs'))

subset(markers, cluster == '6-EX cerebellum granule') %>% .$gene

plot_genes <- subset(markers, cluster == '6-EX cerebellum granule') %>%
  top_n(20, wt=avg_logFC) %>% .$gene


# plot_genes <- c('Gabra6', 'Prox1', 'Mki67', 'Gfap', 'Vim', 'Nes', 'Dlx', 'Trp73', 'Reln')
for(cur_cluster in unique(markers$cluster)){
  print(cur_cluster)
  plot_genes <- subset(markers, cluster == cur_cluster) %>%
    top_n(20, wt=avg_logFC) %>% .$gene

    p <- DotPlot(seurat_obj, group.by='clusternum_anno', features=plot_genes) +
      coord_flip() + RotatedAxis() + scale_color_gradientn(colors=rev(viridis(256))) + ylab('') + xlab('')

    pdf(paste0(fig_dir, 'marker_DEGs/', gsub('/', '-', cur_cluster), '_dotplot_markers.pdf'), width=12, height=6, useDingbats=FALSE)
    print(p)
    dev.off()
}





plot_genes <- c('Tfap2d', 'Slc17a6')

p <- DotPlot(seurat_obj, group.by='clusternum_anno', features=plot_genes) +
  coord_flip() + RotatedAxis() + scale_color_gradientn(colors=rev(viridis(256))) + ylab('') + xlab('')

pdf(paste0(fig_dir, 'test_dotplot_markers.pdf'), width=12, height=4, useDingbats=FALSE)
print(p)
dev.off()

```




















Check ODC subclusters to see if there's any weird doublet signatures:

```{r eval=FALSE}

seurat_odc <- subset(seurat_obj, class %in% c('OPC', 'ODC'))

#################################################################################
# re-analyze this subset
#################################################################################

seurat_odc <- FindVariableFeatures(seurat_odc, nfeatures=2000)
VariableFeatures(seurat_odc) <- VariableFeatures(seurat_odc)[!grepl("^mt-", VariableFeatures(seurat_odc))]
seurat_odc <- RunPCA(seurat_odc)
seurat_odc <- RunHarmony(seurat_odc, dims=1:20, group.by='SampleID')
seurat_odc <- RunUMAP(seurat_odc, reduction='harmony', dims = 1:30, n.neighbors=15L, min.dist=0.25)
seurat_odc <- FindNeighbors(seurat_odc, dims=1:15, reduction='harmony', annoy.metric='cosine')
seurat_odc <- FindClusters(seurat_odc, resolution = 0.1, algorithm=4)


p1 <- DimPlot(seurat_odc,  group.by='seurat_clusters', label=TRUE) + NoLegend()+
  umap_theme

pdf(paste0(fig_dir, 'umap_odc_subclusters.pdf'), width=5, height=5)
p1
dev.off()


markers <- c('Rgs5', 'Mybpc1', 'Dnah11', 'Slc47a1', 'Slc6a13','Csf1r', 'Cx3cr1', 'Cd163', 'Tnc', 'Gfap', 'Aqp4', 'Mobp', 'Mog', 'Pdgfra', 'Slc17a7', 'Rorb', 'Themis', 'Nrgn', 'Gad2', 'Vip', 'Pvalb', 'Sst', 'Lamp5')

plots <- VlnPlot(seurat_odc, features=markers, split.by='DX', combine=FALSE)

for(i in 1:length(plots)){
  plots[[i]] <- plots[[i]] +scale_fill_manual(values=sample_color.scheme)
}

pdf(paste0(fig_dir, 'vlnplot_odc_celltype_markers.pdf'), width=6, height=3, useDingbats=FALSE)
plots
dev.off()



```

Plot with color scheme:

```{r eval=FALSE}

load('~/swaruplab/smorabit/analysis/FIRE_mouse_2021/4-conditions/data/color_scheme_4-conditions.rda')

p1 <- DimPlot(seurat_obj, reduction='paga_umap', group.by='clusternum_anno', label=TRUE) +
  scale_color_manual(values=cluster_colors_all) + umap_theme


pdf(paste0(fig_dir, 'umap_clusters_annotated_colors.pdf'), width=9, height=9)
p1 + NoLegend()
dev.off()




```
